A Decision Procedure for String Constraints with String-Integer Conversion and Flat Regular Constraints

### 2021-05-18 FMCAD2021/6_impl_exp.tex
experimental results

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
% Merge bound and unbound 
\begin{table*}[]
    \label{table:arithmetic}
    \caption{Results of Z3, CVC4 and $\paexp$-Solver on arithmetic benchmark}
    \centering
    \begin{tabular}{cc|cc|cc|cc}
        \multicolumn{1}{l}{} &  & \multicolumn{2}{c|}{Z3} & \multicolumn{2}{c|}{CVC4} & \multicolumn{2}{c}{$\paexp$-solver} \\
        \multicolumn{1}{l}{} &  & number & avg & number & avg & number & avg \\ \hline
        \multirow{4}{*}{2-3-3-4} & SAT & 56 & 0.4 & 42 & 2.3 & 64 & 0.4 \\
         & UNSAT & 69 & \textless{}0.1 & 72 & \textless{}0.1 & 89 & \textless{}0.1 \\
         & B-UNSAT & \multicolumn{1}{l}{} & \multicolumn{1}{l|}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l|}{} & 47 & 9.5 \\
         & TIMEOUT & 75 &  & 86 &  & 0 &  \\ \hline
        \multirow{4}{*}{3-4-4-5} & SAT & 33 & 1.4 & 25 & 2.9 & 52 & 3.3 \\
         & UNSAT & 59 & \textless{}0.1 & 60 & \textless{}0.1 & 88 & \textless{}0.1 \\
         & B-UNSAT & \multicolumn{1}{l}{} & \multicolumn{1}{l|}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l|}{} & 1 & 54.0 \\
         & TIMEOUT & 108 &  & 115 &  & 59 &  \\ \hline
        \multirow{4}{*}{4-5-5-6} & SAT & 35 & 1.8 & 19 & 6.6 & 47 & 22.4 \\
         & UNSAT & 36 & 0.3 & 39 & 0.4 & 72 & 0.1 \\
         & B-UNSAT & \multicolumn{1}{l}{} & \multicolumn{1}{l|}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l|}{} & 0 &  \\
         & TIMEOUT & 129 &  & 142 &  & 81 & 
        \end{tabular}
\end{table*}

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table*}[]
    \label{table:string}
    \caption{Results of Z3, CVC4 and $\paexp$-Solver on string hash function benchmark}
    \centering
    \begin{tabular}{cc|cc|cc|cc|cc}
        &  & \multicolumn{2}{c|}{Z3} & \multicolumn{2}{c|}{CVC4} & \multicolumn{2}{c|}{Trau} & \multicolumn{2}{c}{mysovler} \\
       PATTERN &  & number & time & number & time & number & time & number & time \\ \hline
       \multirow{3}{*}{12345(a)+(b)+} & SAT & 5 & 14.0 & 29 & 8.5 & 3 & \textless{}0.1 & 37 & 9.9 \\
        & UNSAT & 0 &  & 0 &  & 60 & 1.3 & 60 & 47.2 \\
        & FAIL & 95 &  & 71 &  & 32 &  & 3 &  \\ \hline
       \multirow{3}{*}{12345(a)+(b)+6789} & SAT & 11 & 13.0 & 29 & 12.0 & 0 &  & 37 & 10.6 \\
        & UNSAT & 0 &  & 0 &  & 63 & 1.2 & 63 & 50.0 \\
        & FAIL & 89 &  & 71 &  & 37 &  & 0 &  \\ \hline
       \multirow{3}{*}{(a)+(b)+6789} & SAT & 18 & 24.0 & 30 & 9.3 & 2 & \textless{}0.1 & 41 & 16.1 \\
        & UNSAT & 0 &  & 1 & 4.0 & 59 & 2.5 & 59 & 45.8 \\
        & FAIL & 82 &  & 69 &  & 39 &  & 0 &  \\ \hline
       \multirow{3}{*}{12345(\textbackslash{}Sigma)*} & SAT & 82 & 8.7 & 100 & 2.2 & 28 & 5.9 & 100 & 18.5 \\
        & UNSAT & 0 &  & 0 &  & 0 &  & 0 &  \\
        & FAIL & 18 &  & 0 &  & 72 &  & 0 &  \\ \hline
       \multirow{3}{*}{12345(\textbackslash{}Sigma)*6789} & SAT & 60 & 9.3 & 17 & 7.8 & 3 & 0.3 & 100 & 16.0 \\
        & UNSAT & 0 &  & 0 &  & 0 &  & 0 &  \\
        & FAIL & 40 &  & 83 &  & 97 &  & 0 &  \\ \hline
       \multirow{3}{*}{(\textbackslash{}Sigma)*6789} & SAT & 68 & 5.5 & 27 & 13.0 & 24 & 9.0 & 100 & 15.7 \\
        & UNSAT & 0 &  & 0 &  & 0 &  & 0 &  \\
        & FAIL & 32 &  & 73 &  & 76 &  & 0 & 
       \end{tabular}
\end{table*}

>>>>

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
% Merge bound and unbound 
\begin{table*}[]
    \label{table:arithmetic}
        \caption{Experimental Results on ARITHMETIC, \\
    $\#_{\rm prb}$: number of problems, $T_{\rm avg}$: average time in seconds}
    \centering
    \renewcommand{\arraystretch}{1.2}
    \begin{tabular}{|c|c|c|c|c|c|c|c|}
    \hline
        \multirow{2}{*}{Param. }  & \multirow{2}{*}{Output} & \multicolumn{2}{c|}{Z3} & \multicolumn{2}{c|}{CVC4} & \multicolumn{2}{c|}{$\paexp$} \\
        \cline{3-8}
        &  & $\#_{\rm prb}$ & $T_{\rm avg}$  & $\#_{\rm prb}$ & $T_{\rm avg}$  & $\#_{\rm prb}$ & $T_{\rm avg}$  \\ \hline
        \multirow{4}{*}{(2,3,3,4)} & SAT & 56 & {\bf 0.4} & 42 & 2.3 & {\bf 64} & {\bf 0.4} \\
        \cline{2-8}
         & UNSAT & 69 & {\bf \textless{}0.1} & 72 &  {\bf \textless{}0.1} & {\bf 89} & {\bf \textless{}0.1} \\
         \cline{2-8}
         & B-UNSAT & - & - & - & - & 47 & 9.5 \\
         \cline{2-8}
         & TIMEOUT & 75 & - & 86 & - & {\bf 0} & - \\ \hline
         \cline{1-8}
        \multirow{4}{*}{(3,4,4,5)} & SAT & 33 & {\bf 1.4} & 25 & 2.9 & {\bf 52} & 3.3 \\
        \cline{2-8}
         & UNSAT & 59 & {\bf \textless{}0.1} & 60 & {\bf \textless{}0.1} & {\bf 88} & {\bf \textless{}0.1} \\
         \cline{2-8}
         & B-UNSAT & -  & - &  - & -  & 1 & 54.0 \\
         \cline{2-8}
         & TIMEOUT & 108 & - & 115 & - & {\bf 59} & - \\ \hline
         \cline{1-8}
        \multirow{4}{*}{(4,5,5,6)} & SAT & 35 & {\bf 1.8} & 19 & 6.6 & {\bf 47} & 22.4 \\
        \cline{2-8}
         & UNSAT & 36 & 0.3 & 39 & 0.4 & {\bf 72} & {\bf 0.1} \\
         \cline{2-8}
         & B-UNSAT & -  & -  & - & - & 0 & - \\
         \cline{2-8}
         & TIMEOUT & 129 & - & 142 & - & {\bf 81} & -\\
         \hline
        \end{tabular}
\end{table*}

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table*}[]
    \label{table:string}
    \caption{Experimental results on STRINGHASH, \\ $\#_{\rm prb}$: number of problems, $T_{\rm avg}$: average time in seconds}
    \centering
    \renewcommand{\arraystretch}{1.2}
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
    \hline
        \multirow{2}{*} {Pattern}  &  \multirow{2}{*} {Output}  &  \multicolumn{2}{c|}{Z3} & \multicolumn{2}{c|}{CVC4} & \multicolumn{2}{c|}{Trau} & \multicolumn{2}{c|}{$\paexp$} \\
        \cline{3-10}
       &  & $\#_{\rm prb}$ & $T_{\rm avg}$ &  $\#_{\rm prb}$ & $T_{\rm avg}$ & $\#_{\rm prb}$ & $T_{\rm avg}$ &  $\#_{\rm prb}$ & $T_{\rm avg}$ \\ 
       \hline
       \cline{1-10}
       \multirow{3}{*}{$12345(w_1)^+(w_2)^+$} & SAT & 5 & 14.0 & 29 & 8.5 & 3 & {\bf \textless{}0.1} & {\bf 37} & 9.9 \\
         \cline{2-10}
        & UNSAT & 0 & - & 0 & - & {\bf 60} & {\bf 1.3} & {\bf 60} & 47.2 \\
         \cline{2-10}
        & FAIL & 95 & - & 71 & - & 32 & - & {\bf 3} & - \\ \hline
        \cline{1-10}
       \multirow{3}{*}{$12345(w_1)^+(w_2)^+6789$} & SAT & 11 & 13.0 & 29 & 12.0 & 0 & - & {\bf 37} & {\bf 10.6} \\
        \cline{2-10}
        & UNSAT & 0 & - & 0 & - & {\bf 63} & {\bf 1.2} & {\bf 63} & 50.0 \\
         \cline{2-10}
        & FAIL & 89 & - & 71 & - & 37 & - & {\bf 0} & - \\ \hline
        \cline{1-10}
       \multirow{3}{*}{$(w_1)^+(w_2)^+6789$} & SAT & 18 & 24.0 & 30 & 9.3 & 2 & {\bf \textless{}0.1} & {\bf 41} & 16.1 \\
      	 \cline{2-10}
        & UNSAT & 0 & - & 1 & 4.0 & {\bf 59} & {\bf 2.5} & {\bf 59} & 45.8 \\
         \cline{2-10}
        & FAIL & 82 &  & 69 &  & 39 &  & {\bf 0} &  \\ \hline
        \cline{1-10}
       \multirow{3}{*}{$12345\Sigma^*_{\sf num}$} & SAT & 82 & 8.7 & {\bf 100} & {\bf 2.2} & 28 & 5.9 & {\bf 100} & 18.5 \\
        \cline{2-10}
        & UNSAT & 0 & - & 0 & - & 0 & - & 0 & - \\
         \cline{2-10}
        & FAIL & 18 & - & {\bf 0} & - & 72 & - & {\bf 0} & - \\ \hline
        \cline{1-10}
       \multirow{3}{*}{$12345\Sigma^*_{\sf num}6789$} & SAT & 60 & 9.3 & 17 & 7.8 & 3 & {\bf 0.3} & {\bf 100} & 16.0 \\
        \cline{2-10}
        & UNSAT & 0 & - & 0 & - & 0 & - & 0 & - \\
         \cline{2-10}
        & FAIL & 40 & - & 83 & - & 97 & - & {\bf 0} & - \\ \hline
        \cline{1-10}
       \multirow{3}{*}{$\Sigma^*_{\sf num}6789$} & SAT & 68 & 5.5 & 27 & 13.0 & 24 & {\bf 9.0} & {\bf 100} & 15.7 \\
        \cline{2-10}
        & UNSAT & 0 & - & 0 & - & 0 & - & 0 & - \\
         \cline{2-10}
        & FAIL & 32 & - & 73 & - & 76 & - & {\bf 0} &- \\
        \hline
       \end{tabular}
\end{table*}
